\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-04-12 paper/manuscript.tex
plot with snapshot dates

@@

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 29 11:30:05 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lllr}
		\hline
		City & snapshotPrior & electionDay & daysToElection \\ 
		\hline
		Attica & 2015-08-01 & 2015-11-03 & 94 \\ 
		Cornersville & 2015-10-18 & 2015-11-03 & 16 \\ 
		Frankfort & 2015-10-18 & 2015-11-03 & 16 \\ 
		Huntingburg & 2015-10-30 & 2015-11-03 & 4 \\ 
		Indianapolis & 2015-10-16 & 2015-11-03 & 18 \\ 
		Lake Station & 2015-10-29 & 2015-11-03 & 5 \\ 
		Linton & 2015-08-01 & 2015-11-03 & 94 \\ 
		Madison & 2015-09-05 & 2015-11-03 & 59 \\ 
		Mitchell &  & 2015-11-03 &  \\ 
		Monticello & 2015-09-08 & 2015-11-03 & 56 \\ 
		North Vernon & 2015-11-03 & 2015-11-03 & 0 \\ 
		Richmond & 2015-10-31 & 2015-11-03 & 3 \\ 
		Rockport & 2015-10-21 & 2015-11-03 & 13 \\ 
		South Bend & 2015-11-01 & 2015-11-03 & 2 \\ 
		Union City & 2015-09-25 & 2015-11-03 & 39 \\ 
		Winchester & 2015-10-26 & 2015-11-03 & 8 \\ 
		\hline
	\end{tabular}
	\caption{Closest snapshots to election day} 
\end{table}

>>>>

\subsection{Survival model}
The existence of individual documents on municipal government websites can be though of as a survival process. No document stays on a website forever, and it appears to be a reasonable assumption that as documents get older and thus less relevant, they get replaced. The factors determining the steepness of the survival curve are the topic - fire safety regulations likely stay up longer than a bulletin on the annual spring banquet - and the change of party control after an election.

Consequently the covariates include:
\begin{itemize}
\item a categorical independent variable, indicating which topic a document gets assigned to under the expressed agenda model
%\item a variable indicating the change of party control at time $t$
\item is the party that put the document up still present at time $t$
\item interaction term between the two above
\end{itemize}
This will take up a lot of degrees of freedom.

Proportional hazard? If not, then likely rising, although there might be some documents that really do hardly ever get changed, so it should probably fall again after a few years.

Model document being changed vs. being removed as competing risks.

@@

\begin{figure}[!ht]
	\centering
	\caption{Dates of Wayback Machine snapshots. The vertical lines are municipal elections.}
	\label{snapshots}
	\includegraphics[width=\linewidth]{figures/Snapshots.pdf}
\end{figure}
